A Large-Area, Spatially Continuous Assessment of Land Cover Map Error and Its Impact on Downstream Analyses

### 2017-09-04 inst/paper/main.tex
Big commit of figures, and after revising lc figure again in c12.

%\begin{article}
\begin{abstract}
{Land cover maps increasingly underlie research into socioeconomic and environmental patterns and processes, including global change. It is known that map errors impact our understanding of these phenomena, but quantifying these impacts is difficult because many areas lack adequate reference data. We used a highly accurate, high-resolution map of South African cropland to assess 1) the magnitude of error in several current generation land cover maps, and 2) how these errors propagate in downstream studies. We first quantified pixel-wise errors in the cropland classes of four widely used land cover maps at resolutions ranging from 1 to 100 km, then calculated errors in several representative ``downstream'' (map-based) analyses, including assessments of vegetative carbon stocks, evapotranspiration, crop production, and household food security. We also evaluated maps' spatial accuracy based on how precisely they could be used to locate specific landscape features. We found that cropland maps can have substantial biases and poor accuracy at all resolutions (e.g. at 1 km resolution, up to $\sim$45\% underestimates of cropland (bias) and nearly 50\% mean absolute error  (MAE, describing accuracy); at 100 km, up to 15\% underestimates and nearly 20\% MAE). National-scale maps derived from higher resolution imagery were most accurate, followed by multi-map fusion products. Constraining mapped values to match survey statistics proved effective at minimizing bias (provided the statistics are accurate). Errors in downstream analyses could be substantially amplified or muted, depending on the values ascribed to cropland-adjacent covers (e.g. with forest as adjacent cover, carbon map error was 200-500\% greater than in the foundational cropland maps, but $\sim$40\% less for sparse cover types). The average locational error was 6 km (600\%). These findings provide deeper insight into the causes and consequences of land cover map error, including their potential broader regional and policy consequences, and suggest several recommendations for land cover map users.}
\end{abstract}

@@

These problems with land cover products are known \citep{fritz_comparison_2010, fritz_cropland_2011, see_improved_2015, fritz_mapping_2015,verburg_challenges_2011}, and there are a variety of map improvement efforts underway \citep[e.g.][]{fritz_geo-wiki:_2012, estes_platform_2016}. Likewise, the importance of assessing the accuracy of land cover maps is increasingly recognized, and there are well-developed, best-practice guidelines for gathering and using ground-truth samples to robustly quantify map error \citep{foody_status_2002,olofsson_making_2013,olofsson_good_2014,stehman_global_2012}. Because comprehensive, spatially representative ground truth data are typically unavailable for rapidly changing regions \citep{see_improved_2015,kuemmerle_challenges_2013}, what remains an open question is exactly how much the maps researchers typically use deviate from actual land cover, how this affects analyses based on these maps, and how this in turn impacts our understanding of processes being studied.  Our current understanding of map accuracy over such areas is often based on scarce information or top-down "sanity checks" made in comparison to aggregated survey data \citep{yu_meta-discoveries_2014,larsen_taken_2015}.

@@

We used these vector data as a reference for evaluating four land cover products representative of those commonly used in global change studies and related areas of research. The first was South Africa's 30 m resolution 2009 National land cover map \citep[SA-LC][]{sanbi_national_2009}, which is typical of the higher-resolution, Landsat-based maps that are created for individual countries \citep[e.g.][]{fry_completion_2009}. Although global-scale, Landsat-derived maps have recently become available \citep{chen_global_2015}, their reported accuracy for cultivated areas is lower (80-85\% user's accuracy) than those of more intensive, national to sub-national products \citep[e.g. 90\% user's accuracy][]{sweeney_mapping_2015}. The second and third were respectively the 300 m GlobCover 2009 \citep{arino_global_2012} and 500 m resolution MODIS land cover \citep{friedl_modis_2010} data (for 2011, the final year of the reference interval), which are widely used global-scale products \citep[e.g.][]{gross_monitoring_2013, shackelford_conservation_2015}. The fourth dataset was the 1 km Global Land Cover Share (GLC-Share)\citep{fritz_mapping_2015}, which fuses the cropland classes of multiple landcover products (including the three assessed here), with the resulting cropland percentages adjusted until their totals sum to match cropland areas reported in national agricultural statistics (this method also incorporated additional categorical training data collected via crowdsourcing). This ``hybrid-fusion'' approach represents the state of the art in mapping agricultural land cover. Since GeoWiki provides a continuous value of land cover (cropland percentage), which cannot be feasibly converted to a categorical value, we converted all other datasets, including the reference vectors, into comparable 1 km gridded cropland percentages.

@@

We extracted the cropland classes from SA-LC, MODIS, and GlobCover, and converted these into percent cropland estimates at 1 km resolution. Both MODIS and GlobCover had mixed/mosaic classes of cropland and other covers, thus we followed \citet{fritz_mapping_2015} by creating upper, mean, and lower cropland estimates from these classes to produce three versions of the gridded percentages. We used the mean map for the main analysis, but estimated error variability using all three versions (SI).

@@

%\vspace{-1 cm}
We followed this method to create vegetative carbon maps for South Africa. Since our cropland percentage map provided no information on surrounding cover, we developed several variants representing potential surrounding cover types by assigning the average carbon densities of five biomes (forest, secondary forest, shrubland, grassland, and sparse vegetation \citep{ruesch_new_2008}) to the non-cropland fraction of our maps. We multiplied cropland densities by cropland fractions and added these to each of the five other densities multiplied by the residual non-cropland fractions to create five different carbon density maps. We aggregated each carbon map up to 5, 10, 25, 50, and 100 km resolutions for scaling comparisons (SI). To assess carbon estimation error, we subtracted test map-derived carbon maps from those based on the reference map, and calculated bias and accuracy scores using the method described for the cropland maps (see previous section).

Although this analysis ascribed hypothetical carbon densities to non-cropland areas, the selected values represent the range in potential carbon stocks in landscapes containing arable agriculture (error metrics from this analysis defined as pixels containing cropland, pixels without cropland do not influence the results), which allowed us to counterfactually investigate how carbon estimates are affected by the interaction of i) test map errors and ii) the properties of neighboring cover types.

@@

\vspace{-0.5 cm}
\section*{Results}
\vspace{-0.3 cm}
\subsection*{Cropland map errors}
\vspace{-0.2 cm}
Our 1 km reference cropland map indicated that crop fields covered 104,304 km$^2$ (nearly 10\%) of the total study area in the 2009-2011 time period, with corresponding cropland area estimates of 131,390, 82,358, 77,090, and 110,272 (GeoWiki) km$^2$ resulting from the SA-LC, GlobCover, MODIS, and GeoWiki maps, respectively. Cropland area estimates from both the reference and test maps were constant for all levels of aggregation.

Subtracting each test map from the reference maps created pixel-wise residuals, where negative and positive values respectively represent overestimates and underestimates by the test map (Fig. 1A). The most pronounced errors were in the MODIS and GlobCover maps, which showed large positive residuals in the center of the country where cropland is most concentrated (blue areas in Fig. 1A), and negative residuals (red areas) along the eastern and northern margins.
These patterns translated into substantial map bias (Fig. 1B), with GlobCover and MODIS mean error exceeding 45\% and 25\% respectively at 1 km resolution, meaning that each map tends to underestimate cropland by that amount at that resolution. This bias declined with each level of map aggregation, being reduced to nearly 15\% for GlobCover and 5\% for MODIS at 100 km. The magnitude of mean absolute error (MAE) was somewhat higher in all cases. The GeoWiki map, in contrast, was the least biased overall, showing just a $\sim$7\% bias at 1 km and near 0 for all other scales of aggregation, although its accuracy (23\% MAE) was only half as good as SA-LC's at 1 km (11\% MAE), which despite its uniform overestimation bias (Fig. 1A) was the most accurate map at aggregation scales $<10$km. Above this, GeoWiki became slightly more accurate, having $<$5\% MAE at 100 km resolution. The reason GeoWiki had relatively poor accuracy at 1 km resolution was due to the high heterogeneous error pattern, which traded between positive and negative residuals over short distances, thereby inflating MAE at this scale.

\begin{figure*}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\centerline{\includegraphics[width=1\textwidth]{figures/figure1.pdf}}
\vspace{-0.15 cm}
\caption{(A) Errors in the percent cropland estimates resulting from each of the four test maps relative to the reference map at different scale of pixel aggregation. Rows indicate the test map being assessed (by subtraction from the reference map), while columns refer to resolution of aggregation. White indicates areas where areas under communal farmlands or permanent tree crops were removed from analysis. (B) The bias (mean error) and accuracy (mean absolute error [MAE]) of each test map at each scale of aggregation, weighted by the percentage cropland in each cell of the reference map. Bias estimates are indicated by the semi-transparent bars, accuracy (lower is more accurate) by the solid bars, with bar colors coded to specific cropland maps.}
\label{afoto1}
\end{figure*}

@@

%\vspace{-0.75 cm}
%\begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[!h]
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/biases_md_lnorm_gam_mu0.pdf}}
\centerline{\includegraphics[width=.7\textwidth]{figures/biases_md_lnorm_gam_mu0.pdf}}
\caption{The relationship between map accuracy (the mean absolute error) in test maps and the actual cropland cover within agricultural landscapes (reference map pixels having $>$0.5\% cropland), here defined by the boundaries of magisterial districts (n = 345), as fit with a generalized additive model. Prediction curves are color-coded to the different test maps, with the solid line indicating predicted absolute bias, and the lighter shading the standard error of the coefficients.}\label{afoto2}
\end{figure}
%\end{wrapfigure}
%\vspace{-0.75 cm}

@@

The magnitude of carbon errors varied as a function of the carbon density of surrounding cover, as demonstrated by the bias statistics (Fig. 3). Bias was near zero when grassland was the adjacent cover type (SI), as its carbon density is nearly the same as cropland. However, when forest was adjacent then bias was a three- to five-fold multiple of cropland map bias (Fig. 1B). At the most extreme, GlobCover's bias was -276\% at 1 km, but even SA-LC and GeoWiki had biases of 22\% and -50\%, respectively. Bias could be substantial even for the least carbon dense vegetation type (sparse), as evidenced by the 15-25\% mean error at 1 km for MODIS and GlobCover under this class.  The mean bias across the different potential adjacent vegetation classes ranged between -20 for GeoWiki and -123\% for GlobCover at 1 km (with MODIS in between these), while SA-LC's average bias was 11\%.  Biases declined fairly rapidly with aggregation, with all datasets having an average (across cover types) bias magnitude of $<$10\% at $\geq$25 km of aggregation, except for GlobCover, which was -12\% at 100 km (SI).  As with cropland percentages, GeoWiki produced the least biased carbon density estimates above 1 km resolution.

%\vspace{-0.75 cm}
\begin{figure}[!h]
%\begin{wrapfigure}{r}{0.5\textwidth}
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/figure3.pdf}}
\centerline{\includegraphics[width=0.55\textwidth]{figures/figure3.pdf}}
\caption{Biases and accuracies (mean absolute errors) of carbon densities derived from cropland maps, calculated as percents relative to the reference map. Bias estimates (represented by symbols) fall within the semi-transparent floating bars, while accuracies are contained in the solid bars. Bar colors are coded to specific cropland map, symbols indicate which cover type was used to calculate cropland-adjacent carbon density. The bar represents the mean biases calculated across each of the 5 cover types. Shrubland and grassland bias values were near zero, while secondary forest values were close to forest values, and thus these are not shown for display clarity (but see Table S2). MODIS and GlobCover values at 1 km exceeding the plot's Y limits are provided near their truncated tops.}
\label{afoto}
\end{figure}
%\end{wrapfigure}

@@

SA-LC and GeoWiki also resulted in ET errors estimates along the southern and western coasts, but here the tendency was to underestimate ET, while biases in the center of the country were either negligible to absent.  All but MODIS underestimated ET by 5-15\% in the northern tip of the country.  
%
%\vspace{-0.75 cm}
\begin{figure}[h]
\centerline{\includegraphics[width=.6\textwidth]{figures/et_bias_map.pdf}}
\caption{Differences in annual mean evapotranspiration estimates from 29-year runs of the VIC land surface hydrology model when initialized with LAI response curves derived from the reference map, versus those from the four test maps.}\label{afoto}
\end{figure}

@@

%\vspace{-0.5 cm}
\begin{figure}[!ht]
%\vspace{-0.75 cm}
\centerline{\includegraphics[width=0.55\textwidth]{figures/yield_prod_bias.pdf}}
\caption{Bias (mean error) and accuracy (mean absolute error [MAE]) in disaggregated maize yield and production estimates. Bias estimates (represented by symbols) fall within the semi-transparent bars, mean absolute errors in the solid bars, with bar colors coded to specific cropland maps.  Symbols code the different variables (production and yield), normalized to their respective means.}
\label{afoto}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/figure6.pdf}}
\caption{Biases in agent-based model results relative to the district-wise errors (as a percent) in total cropland area, in terms of A) the percent of cropland in each district that was not allocated to any household, B) the land deficit, or the total area of cropland that should have been allocated to households in each district but wasn't (expressed as a percent of total district cropland, as determined by test maps), and C) the food deficit, or the percentage shortfall (relative to the reference simulation) in mean household food production resulting from inadequate cropland allocation. Dot sizes correspond to district numbers, colors represent the land cover map.}
\label{afoto}
\end{figure}

@@

\begin{figure}[!ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/location_offset.pdf}}
\caption{Average nearest neighbor distances (in km) between pixels representing features identified by the reference map versus those identified from the test maps. Bar colors indicate the different features (and thus contributing maps), which were delineated by selecting pixels with values greater than the 90th percentile: densest cropland (solid bars); highest maize yield (medium transparent bars); highest carbon density (most transparent bars).}   
\label{afoto}
\end{figure}

@@

The preceding analyses contributes to existing work investigating land cover map error and its consequences \citep[e.g.][]{fritz_highlighting_2011,verburg_challenges_2011,olofsson_making_2013}. Previous studies have assessed map errors either by using point-based accuracy assessments \citep[e.g.][]{olofsson_making_2013,frey_how_2007-1,foody_status_2002}, by evaluating between-map discrepancies \citep[e.g.][]{fritz_highlighting_2011,fritz_identifying_2008,fritz_comparison_2010}, or by comparing map-derived estimates to aggregated statistics \citep[e.g.][]{larsen_taken_2015,fritz_comparison_2010,yu_meta-discoveries_2014}. A smaller number based their assessments on contiguous ground truth maps, but these covered relatively small regions \cite[$<$3000 km$^2$, or $<$0.03\% of the area covered here;][]{dendoncker_exploring_2008,schmit_limitations_2006}.

>>>>

%\begin{article}
\begin{abstract}
{Land cover maps increasingly underlie research into socioeconomic and environmental patterns and processes, including global change. It is known that map errors impact our understanding of these phenomena, but quantifying these impacts is difficult because many areas lack adequate reference data. We used a highly accurate, high-resolution map of South African cropland to assess 1) the magnitude of error in several current generation land cover maps, and 2) how these errors propagate in downstream studies. We first quantified pixel-wise errors in the cropland classes of four widely used land cover maps at resolutions ranging from 1 to 100 km, then calculated errors in several representative ``downstream'' (map-based) analyses, including assessments of vegetative carbon stocks, evapotranspiration, crop production, and household food security. We also evaluated maps' spatial accuracy based on how precisely they could be used to locate specific landscape features. We found that cropland maps can have substantial biases and poor accuracy at all resolutions (e.g. at 1 km resolution, up to $\sim$45\% underestimates of cropland (bias) and nearly 50\% mean absolute error  (MAE, describing accuracy); at 100 km, up to 15\% underestimates and nearly 20\% MAE). National-scale maps derived from higher resolution imagery were most accurate, followed by multi-map fusion products. Constraining mapped values to match survey statistics may be effective at minimizing bias (provided the statistics are accurate). Errors in downstream analyses could be substantially amplified or muted, depending on the values ascribed to cropland-adjacent covers (e.g. with forest as adjacent cover, carbon map error was 200-500\% greater than in input cropland maps, but $\sim$40\% less for sparse cover types). The average locational error was 6 km (600\%). These findings provide deeper insight into the causes and potential consequences of land cover map error, and suggest several recommendations for land cover map users.}
\end{abstract}

@@

These problems with land cover products are known \citep{fritz_comparison_2010, fritz_cropland_2011, see_improved_2015, fritz_mapping_2015,verburg_challenges_2011}, and there are a variety of map improvement efforts underway \citep[e.g.][]{fritz_geo-wiki:_2012, estes_platform_2016,fritz_mapping_2015}. Likewise, the importance of assessing the accuracy of land cover maps is increasingly recognized, and there are well-developed, best-practice guidelines for gathering and using ground-truth samples to robustly quantify map error \citep{foody_status_2002,olofsson_making_2013,olofsson_good_2014,stehman_global_2012}. Because comprehensive, spatially representative ground truth data are typically unavailable for rapidly changing regions \citep{see_improved_2015,kuemmerle_challenges_2013}, what remains an open question is exactly how much the maps researchers typically use deviate from actual land cover, how this affects analyses based on these maps, and how this in turn impacts our understanding of processes being studied.  Our current understanding of map accuracy over such areas is often based on scarce information or top-down "sanity checks" made in comparison to aggregated survey data \citep{yu_meta-discoveries_2014,larsen_taken_2015}.

@@

We used these vector data as a reference for evaluating four land cover products representative of those commonly used in global change studies and related areas of research (see the SI for an illustration of all five datasets in their original form). The first was South Africa's 30 m resolution 2009 National land cover map \citep[SA-LC;][]{sanbi_national_2009}, which is typical of the higher-resolution, Landsat-based maps that are created for individual countries \citep[e.g.][]{fry_completion_2009}. Although global-scale, Landsat-derived maps have recently become available \citep{chen_global_2015}, their reported accuracy for cultivated areas is lower (80-85\% user's accuracy) than those of more intensive, national to sub-national products \citep[e.g. 90\% user's accuracy][]{sweeney_mapping_2015}. The second and third were respectively the 300 m GlobCover 2009 \citep{arino_global_2012} and 500 m resolution MODIS land cover \citep{friedl_modis_2010} data (for 2011, the final year of the reference interval), which are widely used global-scale products \citep[e.g.][]{gross_monitoring_2013, shackelford_conservation_2015}. The fourth dataset was the 1 km Global Land Cover Share \citep[GLC-Share;][]{latham_global_2014}, which harmonizes and merges the classes of the best available high and medium resolution products for each country/region, providing separate maps for cropland and 10 other thematic classes. Among the datasets included in the GLC-Share's cropland map is the GeoWiki cropland percentage map \citep{waldner_unified_2016, fritz_mapping_2015}, which provided an important input to GLC-Share's cropland layer \citep{latham_global_2014}. The GeoWiki map was also constructed using fusion techniques to merge multiple cropland datasets (including SA-LC, MODIS, and GlobCover), but further calibrated to match cropland areas reported in national agricultural statistics, and validated by crowdsourced volunteers \citep{fritz_mapping_2015}. GLC-Share and the multi-map fusion methodology underlying it (and the GeoWiki map it incorporates) represents a state of the art approach for mapping agricultural land cover. Since GLC-Share provides a continuous value of land cover (cropland percentage), which cannot be feasibly converted to a categorical value, we converted all other datasets, including the reference vectors, into comparable 1 km gridded cropland percentages.

@@

We extracted the cropland classes from SA-LC, MODIS, and GlobCover, and converted these into percent cropland estimates at 1 km resolution. Both MODIS and GlobCover had mixed/mosaic classes of cropland and other covers, thus we followed \citet{fritz_mapping_2015} in creating upper, mean, and lower cropland estimates from these classes to produce three versions of the gridded percentages. We used the mean map for the main analysis, but estimated error variability using all three versions (SI).

@@

%\vspace{-1 cm}
We followed this method to create vegetative carbon maps for South Africa. Since our cropland percentage map provided no information on surrounding cover, we developed several variants representing potential surrounding cover types by assigning the average carbon densities of five biomes \citep[forest, secondary forest, shrubland, grassland, and sparse vegetation;][]{ruesch_new_2008}) to the non-cropland fraction of our maps. We multiplied cropland densities by cropland fractions and added these to each of the five other densities multiplied by the residual non-cropland fractions to create five different carbon density maps. We aggregated each carbon map up to 5, 10, 25, 50, and 100 km resolutions for scaling comparisons (SI). To assess carbon estimation error, we subtracted test map-derived carbon maps from those based on the reference map, and calculated bias and accuracy scores using the method described for the cropland maps (see previous section).

Although this analysis ascribed hypothetical carbon densities to non-cropland areas, the selected values represent the range in potential carbon stocks in landscapes containing arable agriculture (the method for calculating error metrics only affects pixels containing cropland; pixels without cropland do not influence the results), which allowed us to counterfactually investigate how carbon estimates are affected by the interaction of i) test map errors and ii) the properties of neighboring cover types.

@@

\vspace{-0.5 cm}
\section*{Results}
\vspace{-0.3 cm}
\subsection*{Cropland map errors}
\vspace{-0.2 cm}
Our 1 km reference cropland map indicated that crop fields covered 104,304 km$^2$ (nearly 10\%) of the total study area in the 2009-2011 time period, with corresponding cropland area estimates of 131,390, 82,358, 77,090, and 110,272 (GeoWiki) km$^2$ resulting from the SA-LC, GlobCover, MODIS, and GLC-Share maps, respectively. Cropland area estimates from both the reference and test maps were constant for all levels of aggregation.

Subtracting each test map from the reference maps created pixel-wise residuals, where negative and positive values respectively represent overestimates and underestimates by the test map (Fig. 1A). The most pronounced errors were in the MODIS and GlobCover maps, which showed large positive residuals in the center of the country where cropland is most concentrated (blue areas in Fig. 1A), and negative residuals (red areas) along the eastern and northern margins.
These patterns translated into substantial map bias (Fig. 1B), with GlobCover and MODIS mean error exceeding 45\% and 25\% respectively at 1 km resolution, meaning that each map tends to underestimate cropland by that amount at that resolution. This bias declined with each level of map aggregation, being reduced to nearly 15\% for GlobCover and 5\% for MODIS at 100 km. The magnitude of mean absolute error (MAE) was somewhat higher in all cases. The GLC-Share map, in contrast, was the least biased overall, showing just a $\sim$7\% bias at 1 km and near 0 for all other scales of aggregation, although its accuracy (23\% MAE) was only half as good as SA-LC's at 1 km (11\% MAE), which despite its uniform overestimation bias (Fig. 1A) was the most accurate map at aggregation scales $<10$km. Above this, GLC-Share became slightly more accurate, having $<$5\% MAE at 100 km resolution. The reason GLC-Share had relatively poor accuracy at 1 km resolution was due to the highly heterogeneous error pattern, which traded between positive and negative residuals over short distances, thereby inflating MAE at this scale.

\begin{figure*}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\centerline{\includegraphics[width=1\textwidth]{figures/fig1.pdf}}
\vspace{-0.15 cm}
\caption{(A) Errors in the percent cropland estimates resulting from each of the four test maps relative to the reference map at different scale of pixel aggregation. Rows indicate the test map being assessed (by subtraction from the reference map), while columns refer to resolution of aggregation. White indicates areas where areas under communal farmlands or permanent tree crops were removed from analysis. (B) The bias (mean error) and accuracy (mean absolute error [MAE]) of each test map at each scale of aggregation, weighted by the percentage cropland in each cell of the reference map. Bias estimates are indicated by the semi-transparent bars, accuracy (lower is more accurate) by the solid bars, with bar colors coded to specific cropland maps.}
\label{afoto1}
\end{figure*}

@@

%\vspace{-0.75 cm}
%\begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[!h]
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/biases_md_lnorm_gam_mu0.pdf}}
\centerline{\includegraphics[width=.7\textwidth]{figures/fig2.pdf}}
\caption{The relationship between map accuracy (the mean absolute error) in test maps and the actual cropland cover within agricultural landscapes (reference map pixels having $>$0.5\% cropland), here defined by the boundaries of magisterial districts (n = 345), as fit with a generalized additive model. Prediction curves are color-coded to the different test maps, with the solid line indicating predicted absolute bias, and the lighter shading the standard error of the coefficients.}\label{afoto2}
\end{figure}
%\end{wrapfigure}
%\vspace{-0.75 cm}

@@

The magnitude of carbon errors varied as a function of the carbon density of surrounding cover, as demonstrated by the bias statistics (Fig. 3). Bias was near zero when grassland was the adjacent cover type (SI), as its carbon density is nearly the same as cropland. However, when forest was adjacent then bias was a three- to five-fold multiple of cropland map bias (Fig. 1b). At the most extreme, GlobCover's bias was -276\% at 1 km, but even SA-LC and GeoWiki had biases of 22\% and -50\%, respectively. Bias could be substantial even for the least carbon dense vegetation type (sparse), as evidenced by the 15-25\% mean error at 1 km for MODIS and GlobCover under this class.  The mean bias across the different potential adjacent vegetation classes ranged between -20 for GeoWiki and -123\% for GlobCover at 1 km (with MODIS in between these), while SA-LC's average bias was 11\%.  Biases declined fairly rapidly with aggregation, with all datasets having an average (across cover types) bias magnitude of $<$10\% at $\geq$25 km of aggregation, except for GlobCover, which was -12\% at 100 km (SI).  As with cropland percentages, GeoWiki produced the least biased carbon density estimates above 1 km resolution.

%\vspace{-0.75 cm}
\begin{figure}[!h]
%\begin{wrapfigure}{r}{0.5\textwidth}
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/figure3.pdf}}
\centerline{\includegraphics[width=0.55\textwidth]{figures/fig3.pdf}}
\caption{Biases and accuracies (mean absolute errors) of carbon densities derived from cropland maps, calculated as percents relative to the reference map. Bias estimates (represented by symbols) fall within the semi-transparent floating bars, while accuracies are contained in the solid bars. Bar colors are coded to specific cropland map, symbols indicate which cover type was used to calculate cropland-adjacent carbon density. The bar represents the mean biases calculated across each of the 5 cover types. Shrubland and grassland bias values were near zero, while secondary forest values were close to forest values, and thus these are not shown for display clarity (but see Table S2). MODIS and GlobCover values at 1 km exceeding the plot's Y limits are provided near their truncated tops.}
\label{afoto}
\end{figure}
%\end{wrapfigure}

@@

SA-LC and GeoWiki also resulted in ET errors estimates along the southern and western coasts, but here the tendency was to underestimate ET, while biases in the center of the country were either negligible to absent.  All but MODIS underestimated ET by 5-15\% in the northern tip of the country.  
%
%\vspace{-0.75 cm}
\begin{figure}[h]
\centerline{\includegraphics[width=.6\textwidth]{figures/fig4.pdf}}
\caption{Differences in annual mean evapotranspiration estimates from 29-year runs of the VIC land surface hydrology model when initialized with LAI response curves derived from the reference map, versus those from the four test maps.}\label{afoto}
\end{figure}

@@

%\vspace{-0.5 cm}
\begin{figure}[!ht]
%\vspace{-0.75 cm}
\centerline{\includegraphics[width=0.55\textwidth]{figures/fig5.pdf}}
\caption{Bias (mean error) and accuracy (mean absolute error [MAE]) in disaggregated maize yield and production estimates. Bias estimates (represented by symbols) fall within the semi-transparent bars, mean absolute errors in the solid bars, with bar colors coded to specific cropland maps.  Symbols code the different variables (production and yield), normalized to their respective means.}
\label{afoto}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/fig6.pdf}}
\caption{Biases in agent-based model results relative to the district-wise errors (as a percent) in total cropland area, in terms of A) the percent of cropland in each district that was not allocated to any household, B) the land deficit, or the total area of cropland that should have been allocated to households in each district but wasn't (expressed as a percent of total district cropland, as determined by test maps), and C) the food deficit, or the percentage shortfall (relative to the reference simulation) in mean household food production resulting from inadequate cropland allocation. Dot sizes correspond to district numbers, colors represent the land cover map.}
\label{afoto}
\end{figure}

@@

\begin{figure}[!ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/fig7.pdf}}
\caption{Average nearest neighbor distances (in km) between pixels representing features identified by the reference map versus those identified from the test maps. Bar colors indicate the different features (and thus contributing maps), which were delineated by selecting pixels with values greater than the 90th percentile: densest cropland (solid bars); highest maize yield (medium transparent bars); highest carbon density (most transparent bars).}   
\label{afoto}
\end{figure}

@@

The preceding analyses contributes to existing work investigating land cover map error and its consequences \citep[e.g.][]{fritz_highlighting_2011,verburg_challenges_2011,olofsson_making_2013}. Previous studies have assessed map errors either by using point-based accuracy assessments \citep[e.g.][]{olofsson_making_2013,frey_how_2007,foody_status_2002}, by evaluating between-map discrepancies \citep[e.g.][]{fritz_highlighting_2011,fritz_identifying_2008,fritz_comparison_2010}, or by comparing map-derived estimates to aggregated statistics \citep[e.g.][]{larsen_taken_2015,fritz_comparison_2010,yu_meta-discoveries_2014}. A smaller number based their assessments on contiguous ground truth maps, but these covered relatively small regions \cite[$<$3000 km$^2$, or $<$0.03\% of the area covered here;][]{dendoncker_exploring_2008,schmit_limitations_2006}.
